Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters

### 2023-06-28 report/report.tex
adjusted comments

However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.
\pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}
\nm{Keep the current motivation for using company descriptions and then only later mention that we can also add other features?}

@@

\section{Results}
\nm{Rewrite clustering section for the new results, keep location recommendation results as they are?}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/clustering_results.png}
    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering. The company descriptions and industries were used as features.}
    \label{fig:t-sne-agglomerative}
\end{figure}

>>>>

However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.
\pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}
\nm{We keep the current motivation for using company descriptions and then only later mention that we can also add other features}

@@

\section{Results}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/clustering_results.png}
    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering. The company descriptions and industries were used as features.}
    \label{fig:t-sne-agglomerative}
\end{figure}
